自动微分以及它在物理模拟中的应用\fivestar

### 2021-04-27 paper/paper.tex
update ack
update

感谢王磊老师的讨论以及计算设备的支持。

@@

\title{Automatic differentiation in physics simulation $^{\ast}$}%{\efundlink}

\efund{Project supported by ...\\}

@@

\small Automatic differentiation is a technology to differentiate a computer program automatically. It is known to many people for its use in machine learning in recently decades. Nowadays, researchers are becoming more and more aware of the its importance in scientific computing, among which physics simulation is one of the most important yet challenging issue. It is important because it involves many important issues in fields such as chaos, electromagnetism, seismic and oceanographic, while it is challenging because these applications often requires a lot computing time and space. This paper will review several automatic differentiation strategies for differentiating physics simulations, and compare their pros and cons. These methods include adjoint state methods, forward mode automatic differentiation, reverse mode automatic differentiation and reversible programming automatic differentiation.

>>>>

感谢王磊老师的讨论以及计算设备的支持。
感谢彩云天气 CTO 苑明理老师关于自动微分关于自动微分在天气预报中应用的讨论。

@@

\title{Automatic differentiation and its applications in physics simulation $^{\ast}$}%{\efundlink}

\efund{\\}

@@

\small Automatic differentiation is a technology to differentiate a computer program automatically. It is known to many people for its use in machine learning in recent decades. Nowadays, researchers are becoming increasingly aware of its importance in scientific computing, especially in the physics simulation. Differentiating physics simulation can help us solve many important issues in chaos theory, electromagnetism, seismic and oceanographic. Meanwhile, it is also challenging because these applications often require a lot of computing time and space. This paper will review several automatic differentiation strategies for physics simulation, and compare their pros and cons. These methods include adjoint state methods, forward mode automatic differentiation, reverse mode automatic differentiation, and reversible programming automatic differentiation.
